\vfill A Survey of Web Testing Frameworks and a Workflow for Testing Javascript Applications

### 2014-05-12 Paper/paper.tex
Intern IO work, Headless browsers work

%- TDD, BDD, Object methods
Intern uses Chai.js for assertion methods but has it built-in as opposed to Mocha in which the developer had to get it themselves. This gives the developer access to Expect, Assert, and Intern's Object testing methods.

\todo{Add test code here!}

@@

Intern offered a one-stop shop for all of our testing needs but fell short when it came to configuring it for our Node.js server setup. If we had a more traditional web application setup with a seperate server that served normal HTML pages, Intern.io would have likely been our go-to tool for all of our testing needs.

@@

% Browser Testing! Code
\subsubsection{Selenium\cite{Selenium}}
Selenium is an automated browser input runner. It is one of the only automated browser runners and certainly the most prominent. A developer can write code that will cause Selenium to drive a browser's input and assert expectations. On it's own Selenium has very minimal testing usage. It lacks a test reporting mechanism and only offers output in two forms: 1) No output at all, a browser window will open, input will be generated, and the window will close, or 2) the browser will exit with a cryptic error printed to the console. It is up to the developer to include print statements as to what is happening at any given time, what test is being run, and what the results are.

@@

\subsubsection{PhantomJS\cite{PhantomJS}}
% Too much.
%- Really great though, could be useful if needed.
%- Slow
%- FULL DOM/Browser emulation

\subsubsection{ZombieJS\cite{ZombieJS}}
%- Lightweight
%- Headless
%- NOT Full DOM emulation

@@

% -- Extension to all of PX?
% -- Extension to non-proprietary open-source project

>>>>

%-AMD
Intern uses Asynchronous Module Definition (AMD) form which is something we'd not seen before. Where this comes into play is merely in what used to be ``require(...)''. Instead of seperately requiring modules, the entire program is wrapped in a ``define([...])'' block that passes modules as parameters to an overarching function. That will make more sense after an example:
\begin{lstlisting}
// Intern
define([
    'intern!object',
    'intern/chai!assert',
    'app/hello'
], function (registerSuite, assert, hello) {
  // Test code here
});

// CommonJS, what Node.js uses 
var registerSuite = require('intern/object');
var assert = require('intern/chai/assert');
var hello = require('app/hello');

// Test code here

// Another way to write CommonJS so that it's not global scope, used frequently
(function () {
  var registerSuite = require('intern/object');
  var assert = require('intern/chai/assert');
  var hello = require('app/hello');

  // Test code here
} ());
\end{lstlisting}

Using either style you get access to the modules outlined. AMD form offers a tighter, more straightforward way to look at module loading in addtiion to being better supported and having fewer gotchas. \cite{AMDInfo} Intern offers support for CommonJS modules but strongly recommends switching to AMD styles for your project. We chose to keep out CommonJS format because of the maturity of the evaluation project.

%- TDD, BDD, Object methods
Intern uses Chai.js for assertion methods but has it built-in as opposed to Mocha in which the developer had to get it themselves. This gives the developer access to Expect, Assert, and Should testing methods. In addition to the various assertion styles, Intern offers three different testing interfaces: TDD, BDD, and Object. These testing interfaces effect how the general layout of test code looks. Here's a very quick example of the different layouts:
\begin{lstlisting}
// TDD
suite('TDD Suite', function () {
  test('test 1', function () {
    ...
  });
}

// BDD
describe('BDD Suite', function () {
  it('should be test 1', function () {
    ...
  });
}

// Object
registerSuite({
  name: 'Object Suite',

  'test 1' : function () {
    ...
  }
)
\end{lstlisting}

The ability to mix assertion styles with testing interfaces provides the most diverse ways of writing tests that we've found. Some testing interfaces seems to fit better with certain assertion styles, but there's no restrictions on which can be used with which.

@@

Intern offered a one-stop shop for all of our testing needs but fell short when it came to configuring it for our Node.js server setup. If we had a more traditional web application setup with a seperate server that served normal HTML pages, Intern would have likely been our go-to tool for all of our testing needs.

@@

\subsubsection{Selenium\cite{Selenium}}
Selenium is an automated browser input runner. It is one of the only automated browser runners and certainly the most prominent. A developer can write code that will cause Selenium to drive a browser's input and assert expectations. On it's own Selenium has very minimal testing usage. It lacks a test reporting mechanism and only offers output in two forms: 1) No output at all, a browser window will open, input will be generated, and the window will close, or 2) the browser will exit with a cryptic error printed to the console. It is up to the developer to include print statements as to what is happening at any given time, what test is being run, and what the results are.

@@

\todo{How important is having these? Mention as an option but don't go into detail?}
\subsubsection{Headless Browsers}
In an attempt to speed up UI testing, which is notoriously slow, there have been efforts to create ``headless'' browsers which behave like normal browsers except that there's no display element. They emulate the DOM and skip the display phase. We opted to stick with visual browsers due to time constraints and the enjoyment of watching the tests execute.

Nonetheless, we still looked at two options that we will outline briefly below for other developer's reference.

\paragraph{PhantomJS\cite{PhantomJS}}
The reigning king of headless browsers is PhantomJS. PhantomJS is a headless browser written using WebKit, which is what most of the web is based on. This means that running PhantomJS is nearly indistinuishable from a normal browser to any testing code.

There are, however, a couple problems with PhantomJS. It is generally fairly verbose when it comes to writing the scripts that run your commands. It is also not a testing tool, it is a headless WebKit. The distinction here is that PhantomJS does not have any assert functionality built-in and thus requires the developer to find and use their own assertion library.

The difference between PhantomJS and ZombieJS, which I talk about in the next section, is akin to the difference between Selenium and Nightwatch. PhantomJS is heavier duty and requires an additional set of testing tools whereas ZombieJS is lightweight and has assertions built-in.
% Too much.
%- Really great though, could be useful if needed.
%- Slow
%- FULL DOM/Browser emulation

\paragraph{ZombieJS\cite{ZombieJS}}
ZombieJS is often the other go-to for headless browsers. ZombieJS is not a WebKit implementation but rather a simple DOM emulator. This means that certain tests may not be as accurate as they could be with PhantomJS.

Where ZombieJS shines is in its simplicity and brevity. Much like Nightwatch, calls are chained together to create a flow of calls that generally end with assertions.

\begin{lstlisting}
// Zombie.js website's example code
var Browser = require("zombie");
var assert = require("assert");

// Load the page from localhost
browser = new Browser()
browser.visit("http://localhost:3000/", function () {

  // Fill email, password and submit form
  browser.
    fill("email", "zombie@underworld.dead").
    fill("password", "eat-the-living").
    pressButton("Sign Me Up!", function() {

      // Form submitted, new page loaded.
      assert.ok(browser.success);
      assert.equal(browser.text("title"), "Welcome To Brains Depot");

    })
});
\end{lstlisting}

Developers like ZombieJS syntax so much that there exists a wrapper that uses ZombieJS's API around PhantomJS. \cite{ZombiePhantom}

ZombieJS offers a lightweight solution to headless browser testing, but does not have the same depth of features as PhantomJS or the same assurances that your tests do exactly what they would do in a browser with a head.

%- Lightweight
%- Headless
%- NOT Full DOM emulation

@@

% -- Extension to all of PX?
% -- Extension to non-proprietary open-source project
% -- Headless browsers
